Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-02-05 paper.tex
Fixed PyTorch reference

A notable exception to this is the \emph{DocCreator} image synthesizing tool \cite{ref_DocCreator}, which is targeted towards creating synthetic images that mimic common corruptions seen in document collections.
\emph{DocCreator} differs from \emph{Augraphy} in several crucial ways.
The first difference is that \emph{DocCreator}'s augmentations are meant to imitate those seen in historical (e.g., ancient or medieval) documents, while \emph{Augraphy} is intended to replicate noise caused by office room procedures.
\emph{DocCreator} was also written in the C++ programming language as a monolithic what-you-see-is-what-you-get tool, and does not have a scripting or API interface to enable use in a broader machine learning pipeline.
\emph{Augraphy}, in contrast, is written in Python and can be easily integrated into machine learning model development and evaluation pipelines, alongside other Python packages like PyTorch \cite{ref_PyTorch}.

>>>>

A notable exception to this is the \emph{DocCreator} image synthesizing tool \cite{ref_DocCreator}, which is targeted towards creating synthetic images that mimic common corruptions seen in document collections.
\emph{DocCreator} differs from \emph{Augraphy} in several crucial ways.
The first difference is that \emph{DocCreator}'s augmentations are meant to imitate those seen in historical (e.g., ancient or medieval) documents, while \emph{Augraphy} is intended to replicate noise caused by office room procedures.
\emph{DocCreator} was also written in the C++ programming language as a monolithic what-you-see-is-what-you-get tool, and does not have a scripting or API interface to enable use in a broader machine learning pipeline.
\emph{Augraphy}, in contrast, is written in Python and can be easily integrated into machine learning model development and evaluation pipelines, alongside other Python packages like PyTorch \cite{ref_pytorch}.
